Displacement of fishing effort by Large Scale Marine Protected Areas

### 2019-01-10 slides/ERE_lunch.Rmd
Updated slides

---
title: "Displacement of fishing effort by Large Scale Marine Protected Areas"
author:
  - Juan Carlos Villaseñor-Derbez^1^
  - John Lynham^2^
institute:
  - ^1^Bren School of Environmental Science and Management, UC Santa Barbara
  - ^2^Department of Economics, University of Hawaii at Manoa
date: "5/10/2018"
output: 
  beamer_presentation: 
    citation_package: biblatex
    slide_level: 2
    theme: Berkeley
bibliography: references.bib
biblio-style: authoryear
header-includes:
  - \usepackage{booktabs}
---

>>>>

---
title: "Displacement of fishing effort by Large Scale Marine Protected Areas"
author:
  - Juan Carlos Villaseñor-Derbez^1^
  - John Lynham^2^
institute:
  - ^1^Bren School of Environmental Science and Management, UC Santa Barbara
  - ^2^Department of Economics, University of Hawaii at Manoa
date: "5/10/2018"
output: 
  beamer_presentation: 
    citation_package: biblatex
    slide_level: 2
bibliography: references.bib
biblio-style: authoryear
header-includes:
  - \usepackage{booktabs}
---
